parameters

### 2020-01-16 manuscript/manuscript.Rmd
combins update

# combinations table
combins <- expand.grid(params)

```

>>>>

# combinations table
combins <- expand.grid(params)
#combins$model %in% c("lstm_base", "lstm_pool") & combins$feature_extraction != "embeddingLSTM"

combins <- combins %>%
  #filter(combins$model %in% c("lstm_base", "lstm_pool") & feature_extraction != "embeddingLSTM") %>%
  arrange(model)
```
